I mean really clean the pheno and get to know the hell of the samples

### 2019-11-06 scripts/01_clean_pheno.Rmd
update

final_pheno %>% 
  write_csv('../data/cleaned_pheno/final_pheno.csv')
```

>>>>

final_pheno %>% 
  write_csv('../data/cleaned_pheno/final_pheno.csv')

# write out the meta data info with tox and CR in each of the table
final_pheno %>% 
  select(Sampleid, Toxicity) %>% 
  write_csv('../data/cleaned_pheno/tox_metadata.csv')
```
